%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Data Analyst} % Job title
{Zavient} % Organization
{Moscow, Russian Federation} % Location
{October 2019 - December 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {SEM. Managing/optimizing Google Ads, Bing Ads accounts.}
    \item {Creation of an automatic bid adjustment strategies based on the statistical arbitrage concept. (via Google Ads scripts embedded into accounts)}
    \item {Hypothesis testing of the Keywords distributions based on historical data (sample: https://github.com/bluella/keywords-distribution-analysis)}
    \item {Automation of Negative Keywords generation via Query Reports analysis}
    \item {Bulk modifications of Ads, Campaigns via scripts.}
  \end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Research Consultant} % Job title
    {WorldQuant} % Organization
    {Moscow, Russian Federation} % Location
    {April 2015 - September 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing financial market signals.}
        \item {Top one by actual weight(money invested) since October 2016 to April 2019. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python developer, Co-founder} % Job title
    {Canaree Project} % Organization
    {Moscow, Russian Federation} % Location
    {Nov. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a media analysis tool that helps get insights for better product and media strategizing, as well as helps fighting fake news.}
        \item {Monitoring popularity}
        \item {Determining social mood (sentiments) and it's tendencies}
        \item {Using ML models to forecast further success of product in a social field}
        \item {Speaking more technically we are getting posts with hashtag of interest.
        Than we are processing them to calculate daily statistics like number of posts,
        likes, comments, average sentiment, etc. and store all of them in our database.
        Then when clients come to our website, we are able to draw beautiful graphs and
        diagrams based on statistics calculated before
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Prokhorov General Physics Institute} % Organization
    {Moscow, Russian Federation} % Location
    {Oct. 2016 - Exp. Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigation of the characteristics of a local adaptive light protective filter.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Laboratory Assistant} % Job title
    {Lomonosov Moscow State University (MSU)} % Organization
    {Moscow, Russian Federation} % Location
    {Jan. 2016 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Diagnostics of thermostat malfunctions.}
        \item {Fuse replacement}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
